Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-15 robdml.tex
tex

It \emph{must} be acknowledged that the high R@1 performance of our method
largely stems from the source triplet sampling strategy, namely Softhard,
instead of our contribution.
%
In terms of the overall performance, our method can achieve the highest ERS at
the lowest performance drop in R@1 under a fixed training cost.
%
The existing methods are overwhelmingly outperformed by our method in overall
performance.

For adversarial training of a DML model, selectiveness on both benign and
adversarial training samples is crucial for preventing model collapse, and
achieving good performance on both types of samples.
%
HM is a flexible tool for specifying such a ``selection'',
while LGA is a selection rule for adversarial examples.
%
ICS loss term helps the model exploit more information from the
given sextuplet.

Further discussions on experiments, technical details, limitations and societal
impact are presented in the supplementary document.

>>>>

It \emph{must} be acknowledged that the high R@1 performance of our method
largely stems from the source triplet sampling strategy, \ie, Softhard,
instead of our contribution.
%
But the other methods cannot reach the same level of robustness with the same
sampling strategy.
%
Besides, our method achieves the highest ERS at
the lowest R@1 drop under a fixed training cost.
%
Thus, our proposed method overwhelmingly outperforms the existing defenses
in overall performance.
%

Conclusively, being selective on both benign and
adversarial training samples is crucial for preventing model collapse, and
achieving good performance on both types of samples.
%
HM is a flexible tool for specifying such ``selection'' of adversarial
examples, while LGA can be interpreted as a concrete ``selection''.
%
ICS loss further exploits the given sextuplet.

Further discussions, technical details, and limitations, \etc,
are presented in the supplementary document.
